Digital Analysis of Paintings

### 2014-04-29 paper.tex
Add some more details.
Also changed to a less sexist picture. Hopper > Lenna.

To allow image classification across different scales, one needs a dyadic
space; a space in which there are a collection of regions of different scales,
where a region at one scale can also be viewed as the union of regions in a
smaller scale. Figure~\ref{fig:dyadic-image} shows an example of this where the
large regions show only a pixalated view of the image and the smallest the
individual pixels of the image.

\begin{figure}[ht]
\centering
\subfloat[$C=8$]{\includegraphics[width=0.1\textwidth]{dyadic_2.png}}%
\hspace{.2in}%
\subfloat[$C=32$]{\includegraphics[width=0.1\textwidth]{dyadic_4.png}}%
\hspace{.2in}%
\subfloat[$C=128$]{\includegraphics[width=0.1\textwidth]{dyadic_8.png}}%
\hspace{.2in}%
\subfloat[$C=512$]{\includegraphics[width=0.1\textwidth]{dyadic_16.png}}%
\caption{Example of dyadic space using the standard Lenna image (512x512
pixels) at different dyadic scales ($C$), note how the picture becomes less
pixalated at higher scales}
\label{fig:dyadic-image}
\end{figure}

>>>>

To allow image classification across different scales, one needs a dyadic
space; a space in which there are a collection of regions of different scales,
where a region at one scale can also be viewed as the union of regions in a
smaller scale. Figure~\ref{fig:dyadic-image}\footnote{The photograph is
property of the U.S. Federal Government, and is therefore in the public
domain} shows an example of this where the large regions show only a pixalated
view of the image and the smallest the individual pixels of the image.

\begin{figure}[ht]
\centering
\subfloat[$C=8$]{\includegraphics[width=0.1\textwidth]{dyadic_2.png}}%
\hspace{.2in}%
\subfloat[$C=32$]{\includegraphics[width=0.1\textwidth]{dyadic_4.png}}%
\hspace{.2in}%
\subfloat[$C=128$]{\includegraphics[width=0.1\textwidth]{dyadic_8.png}}%
\hspace{.2in}%
\subfloat[$C=512$ (Original Size)]{\includegraphics[width=0.1\textwidth]{dyadic_16.png}}%
\caption{Example of dyadic space using an image of Grace Hopper (512x512
pixels) at different dyadic scales ($C$), note how the picture becomes less
pixalated at higher scales}
\label{fig:dyadic-image}
\end{figure}

A natural interpretation of multifractal analysis needs to be based on wavelet
leaders, which allows an estimation of the multifractal spectrum of an image.
The wavelet coefficients at finer scales within a small neighbourhood are used
to renormalise the wavelet coefficients at a given scale.

This is all theoretically very sound, but in practise it cannot be used on
paintings without some modifications, mainly due to the fact that digital
objects do not have an infinite resolution. So the analysis is slightly
simplified to account for this to provide a fair estimation of the real
analysis.

This technique was applied to several different works, but the most interesting
of there was the Princeton experiment, where an artist produced seven distinct
small paintings using different materials. Two weeks later the artist was asked
to produce replicas as close to the original as possible.

Both the originals and replicas were scanned at a very high resolution to allow
this analysis to be as detailed as possible.

The results showed that, systematically, the textures of the replicas were
globally more regular and smoother than the originals. However, it should be
noted that getting these results required the expert selection of sections to
analyse and the a posteriori selection of the range of scales for wavelet
leaders.

With promising results shown from this experimentation, attention was turned to
a norm for painting analysis: Van Gogh. Rather than consider the global state
of the canvas, each image was split into smaller sections for the analysis, as
paintings very rarely have the same texture globally.

This analysis was used to try and place paintings in a date region and detect
forgeries. The results shown for dating paintings into a period show some
promising results, where the majority of paintings were correctly clustered
into their correct periods. For detecting forgeries the results are promising,
but one forgery slips by when it was noticed by experts.

This technique is agnostic to the colour space and the authors do apply it to
several different colour spaces, including black-white intensity, \gls{RGB} and
\gls{HSL}.

There is a lot of expert knowledge which cannot be automated or, where it can
be, is very arbitrary such as blindly selecting patches.

The results from the Princeton experiments are promising, but the
